---
title       : Creating a Virtual Yearbook of the REAL Mafia
subtitle    : Exploring its members' memories and connections
author      : Esteban Lopez
job         : UIUC PhD Candidate, REAL 'General'
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, mathjax]
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## Outline

>1. The Instrument
>2. Exploratory Analysis
>3. The REAL Mafia in a Network context
  - Academic
  - Friendship
>4. Spatial Analysis
>5. The REAL Virtual Yearbook
>6. Memories Semantic Analysis


--- 

## The Instrument

```{r echo=FALSE, results='asis', message=FALSE}
require(googleVis)
table1<-as.data.frame(cbind(c("Identification","Time in REAL","Academics with REAL","REAL Memories and Annecdotes"),c("Name, Country, Affiliation, etc.","Dates, Mafia role, General, sitting, etc.","Research areas, collaboration, influences, post-mafia work.","CU, UIUC, REAL, Geoff")))
names(table1)<-c("Section","Description")
table2<-gvisTable(table1,options=list(width=800, height=300))
cat(unlist(table2$html$chart))
print(table2,tag='chart')

```
<br>

- Sampled REAL Mafia: _400 (aprox.) e-mails sent_
- Number of Respondents REAL Mafia: _104 responded surveys_
- Number of attendants to this event: _120 aprox._ 

--- &vcenter

## The 'Actual' Instrument

<iframe src="https://docs.google.com/forms/d/1B3qXUtLhqH7JSpo1zLH0DZeEzPPt0YIXEMp48NUA0eI/viewform?edit_requested=true" heingt='600px'></iframe>

--- .segue bg:indigo

## Exploratory Analysis

---  &vcenter

## Demographic Frequencies

```{r echo=FALSE, message=FALSE, results='asis',size=6}
require(stargazer)
setwd("/Users/estebanlopez/Documents/001 PhD Material/Work at REAL/25th-Anniversary/Timeline/realVirtualYearbook/")
data<-read.csv("data/data_exploratory.csv")
d2<-cbind(data[,4:6],data[,11])
colnames(d2)[4]<-"Mafia Type"
stargazer(as.matrix(ftable(summary(d2))),type="html",font.size="scriptsize")
```

---  &vcenter

## Initial Country


```{r echo=FALSE, message=FALSE, results='asis'}
setwd("/Users/estebanlopez/Documents/001 PhD Material/Work at REAL/25th-Anniversary/Timeline/realVirtualYearbook/")
data<-read.csv("data/data_exploratory.csv")

data$Current_Country2<-data$Current_Country
data$Country_Origin2<-data$Country_Origin
levels(data$Country_Origin2)[levels(data$Country_Origin2)=="Brasil"]<-"Brazil"
levels(data$Country_Origin2)[levels(data$Country_Origin2)=="US"]<-"USA"
levels(data$Country_Origin2)[levels(data$Country_Origin2)=="Espa\x96a"]<-"Spain"
levels(data$Country_Origin2)[levels(data$Country_Origin2)=="T\x9frkiye"]<-"Turkey"

pie3<-as.data.frame(round(table(data[,"Country_Origin2"]),2))
pie4<-gvisGeoChart(pie3,"Var1","Freq",options=list(width=800, height=500))
cat(unlist(pie4$html$chart))
print(pie4,tag="chart")
```

---  &vcenter

## Current Country

```{r echo=FALSE, message=FALSE, results='asis'}
setwd("/Users/estebanlopez/Documents/001 PhD Material/Work at REAL/25th-Anniversary/Timeline/realVirtualYearbook/")
data<-read.csv("data/data_exploratory.csv")

data$Current_Country2<-data$Current_Country
levels(data$Current_Country2)[levels(data$Current_Country2)=="US"]<-"USA"
levels(data$Current_Country2)[levels(data$Current_Country2)=="Estados Unidos"]<-"USA"
levels(data$Current_Country2)[levels(data$Current_Country2)=="U.S."]<-"USA"
levels(data$Current_Country2)[levels(data$Current_Country2)=="United States"]<-"USA"
levels(data$Current_Country2)[levels(data$Current_Country2)=="Champaign"]<-"USA"
levels(data$Current_Country2)[levels(data$Current_Country2)=="Espa\x96a"]<-"Spain"
levels(data$Current_Country2)[levels(data$Current_Country2)=="Brasil"]<-"Brazil"
levels(data$Current_Country2)[levels(data$Current_Country2)=="M\x8exico"]<-"Mexico"
levels(data$Current_Country2)[levels(data$Current_Country2)=="T\x9frkiye"]<-"Turkey"
levels(data$Current_Country2)[levels(data$Current_Country2)=="Brazil - USA"]<-"Brazil"
pie1<-as.data.frame(round(table(data[,"Current_Country2"]),2))
pie2<-gvisGeoChart(pie1,"Var1","Freq",options=list(width=800, height=500))
cat(unlist(pie2$html$chart))
print(pie2,tag="chart")
```

--- &vcenter

## Duration in REAL

```{r echo=FALSE, message=FALSE, results='asis'}
require(googleVis)
data<-read.csv("data2.csv")
h1<-gvisHistogram(data.frame(data["months_total"]),options=list(width=800, height=350,legend="{position:'top'}",legend.alignment='end'))
print(h1,'chart')
```
- Mafia type by duration:
  - _0-14_: Short term scholars (Spaniards & Brazilian Sandwich Mostly)
  - _14-28_: Long term scholars & Masters
  - _28+_: PhD Students and REAL lovers.

--- .segue bg:indigo

## Academics at REAL

--- &twocol w1:45% w2:35% &vcenter

## 1st most important research area at REAL.
*** =left
```{r echo=FALSE, message=FALSE, results='asis'}
setwd("/Users/estebanlopez/Documents/001 PhD Material/Work at REAL/25th-Anniversary/Timeline/realVirtualYearbook/")
data<-read.csv("data/data_exploratory.csv")
pie1<-as.data.frame(round(table(data$research_1),2))
pie2<-gvisPieChart(pie1,options=list(width=600, height=550,legend="none"))
cat(unlist(pie2$html$chart))
print(pie2,tag="chart")
```

*** =right

>- <strong> within Regional Economic Growth falls:</strong>
    - Neoclasical, Endogenous & Spatial Growth Models
    - CGEs, static, dynamic and spatial
    - Regional growth and convergence
    - Spatial Policy for Growth and Equity

>- _together Growth, Spatial Econometrics, Housing & Labor make up to 63%_

--- &twocol w1:45% w2:35% &vcenter

## 2nd most important research area at REAL.
*** =left
```{r echo=FALSE, message=FALSE, results='asis'}
data<-read.csv("data2.csv")
pie1<-as.data.frame(round(table(data$research_2),2))
pie2<-gvisPieChart(pie1,options=list(width=600, height=550,legend="none"))
cat(unlist(pie2$html$chart))
print(pie2,tag="chart")
```
*** =right
>- All spatial sciences grow in importance
>- Further survey should have a finer categorization

--- &vcenter

## Productivity by Mafia Type

```{r echo=F,message=FALSE,results='asis'}
#The more time you are at REAL, the more papers you do.
require(doBy)
require(ggplot2)
df<-data.frame(summaryBy(months_total~Mafia_type + working_papers,data=data))

df2<-reshape(df,timevar="Mafia_type",direction="wide",idvar="working_papers",v.names="months_total.mean")

colnames(df2)[2:6]<-levels(factor(df$Mafia_type))
df2<-data.frame(rbind(df2[,1],df2[3,],df2[4,],df2[2,]))

bchart0<-gvisColumnChart(df2,options=list(width=950, height=500, vAxis="{title:'Average No. Months'}",hAxis="{title:'Working Papers at REAL'}"))
print(bchart0,'chart')

#a<-ggplot(df,aes(x=working_papers, y=months_total.mean, group=Mafia_type))
#a + geom_bar(stat="identity", position="dodge",aes(fill=Mafia_type))+labs(y="Months in REAL", x="Number of Working Papers", fill="")+ theme(legend.position="bottom")
```

--- &vcenter

## Productivity by Research Area (1st)

```{r echo=F,message=FALSE,results='asis'}
#The most frequent fields of study (Eco. growth, housing, SpEcon) do mostly 1 or 2-3 papers. 

require(doBy)
require(ggplot2)
df<-data.frame(table(data$research_1,data$working_papers))
names(df)<-c("research_1","working_papers","Freq")

levels(df$research_1)[levels(data$research_1)=="Environmental and Natural Resources"]<-"Environmental"
levels(df$research_1)[levels(data$research_1)=="Innovation and Regional Economic Development"]<-"Reg. Econ. Dev."
levels(df$research_1)[levels(data$research_1)=="New Economic Geography and Evolutionary Economic Geography"]<-"NEG"
levels(df$research_1)[levels(data$research_1)=="New Economic Geography and Evolutionary Economic Geography"]<-"NEG"
levels(df$research_1)[levels(data$research_1)=="Regional Economic Growth"]<-"Econ. Growth"
levels(df$research_1)[levels(data$research_1)=="Regional Housing and Labor Markets"]<-"Housing & Labor Mark."
levels(df$research_1)[levels(data$research_1)=="Spatial Analysis and Geocomputation"]<-"Geocomputation"

df2<-reshape(df,timevar="research_1",direction="wide",idvar="working_papers",v.names="Freq")

colnames(df2)[2:11]<-levels(factor(df$research_1))

bchart<-gvisColumnChart(df2,options=list(width=950, height=500, vAxis="{title:'Frequency'}",hAxis="{title:'Working Papers at REAL'}"))
print(bchart,'chart')


```

--- &vcenter

## Productivity by Research Area (1st) & No. of Months

```{r echo=F,message=FALSE,results='asis'}
#This plot serves to show how much time in average takes to do papers. It seems that those papers that were concentrated in the 1 and 2-3 categories took around 16 months in average to do. In contrast mafia working in less frequent areas seem to have spent more time and also get more papers. This is the case of Interaction and location. In summary, mafia concentrated in fields such as Econ. Growth seem to be characterized by less papers and shorter stays, opositite fields like Location and interaction that are characterized by longer stays but also more papers. 

require(doBy)
require(ggplot2)
df<-data.frame(summaryBy(months_total~research_1 + working_papers,data=data,FUN=mean))
levels(df$research_1)[levels(data$research_1)=="Environmental and Natural Resources"]<-"Environmental"
levels(df$research_1)[levels(data$research_1)=="Innovation and Regional Economic Development"]<-"Reg. Econ. Dev."
levels(df$research_1)[levels(data$research_1)=="New Economic Geography and Evolutionary Economic Geography"]<-"NEG"
levels(df$research_1)[levels(data$research_1)=="New Economic Geography and Evolutionary Economic Geography"]<-"NEG"
levels(df$research_1)[levels(data$research_1)=="Regional Economic Growth"]<-"Econ. Growth"
levels(df$research_1)[levels(data$research_1)=="Regional Housing and Labor Markets"]<-"Housing & Labor Mark."
levels(df$research_1)[levels(data$research_1)=="Spatial Analysis and Geocomputation"]<-"Geocomputation"

df2<-reshape(df,timevar="research_1",direction="wide",idvar="working_papers",v.names="months_total.mean")
colnames(df2)[2:11]<-levels(factor(df$research_1))

bchart1<-gvisColumnChart(df2,options=list(width=950, height=500, vAxis="{title:'Average Number of months'}",hAxis="{title:'Working Papers at REAL'}"))
print(bchart1,'chart')

```

--- &vcenter

## Productivity by Research Area (2nd)

```{r echo=F,message=FALSE,results='asis'}
#Same as in the pie chart, spatial econometrics seem to have concentrated in the 1 and 2-3 productivity section. However, this time Econ. Growth seems to have been more distributed across the productivity levels. 

require(doBy)
require(ggplot2)
df<-data.frame(table(data$research_2,data$working_papers))
names(df)<-c("research_2","working_papers","Freq")

levels(df$research_2)[levels(data$research_2)=="Environmental and Natural Resources"]<-"Environmental"
levels(df$research_2)[levels(data$research_2)=="Innovation and Regional Economic Development"]<-"Reg. Econ. Dev."
levels(df$research_2)[levels(data$research_2)=="New Economic Geography and Evolutionary Economic Geography"]<-"NEG"
levels(df$research_2)[levels(data$research_2)=="New Economic Geography and Evolutionary Economic Geography"]<-"NEG"
levels(df$research_2)[levels(data$research_2)=="Regional Economic Growth"]<-"Econ. Growth"
levels(df$research_2)[levels(data$research_2)=="Regional Housing and Labor Markets"]<-"Housing & Labor Mark."
levels(df$research_2)[levels(data$research_2)=="Spatial Analysis and Geocomputation"]<-"Geocomputation"

df2<-reshape(df,timevar="research_2",direction="wide",idvar="working_papers",v.names="Freq")

colnames(df2)[2:11]<-levels(factor(df$research_2))

bchart<-gvisColumnChart(df2,options=list(width=950, height=500, vAxis="{title:'Frequency'}",hAxis="{title:'Working Papers at REAL'}"))
print(bchart,'chart')

```

--- &vcenter

## Productivity by Research Area (2nd) & No. of Months

```{r echo=F,message=FALSE,results='asis'}
# What seems interesting is that this time those that were choosen as the second areas of specialization seem to have needed more time in general, perhaps because of lesser economics of scale of getting to know another area of expertise. However it mantains that the more you stay in REAL the more you produce papers.
require(doBy)
require(ggplot2)
df<-data.frame(summaryBy(months_total~research_2 + working_papers,data=data,FUN=mean))
levels(df$research_2)[levels(data$research_2)=="Environmental and Natural Resources"]<-"Environmental"
levels(df$research_2)[levels(data$research_2)=="Innovation and Regional Economic Development"]<-"Reg. Econ. Dev."
levels(df$research_2)[levels(data$research_2)=="New Economic Geography and Evolutionary Economic Geography"]<-"NEG"
levels(df$research_2)[levels(data$research_2)=="New Economic Geography and Evolutionary Economic Geography"]<-"NEG"
levels(df$research_2)[levels(data$research_2)=="Regional Economic Growth"]<-"Econ. Growth"
levels(df$research_2)[levels(data$research_2)=="Regional Housing and Labor Markets"]<-"Housing & Labor Mark."
levels(df$research_2)[levels(data$research_2)=="Spatial Analysis and Geocomputation"]<-"Geocomputation"

df2<-reshape(df,timevar="research_2",direction="wide",idvar="working_papers",v.names="months_total.mean")
colnames(df2)[2:11]<-levels(factor(df$research_2))

bchart1<-gvisColumnChart(df2,options=list(width=950, height=500, vAxis="{title:'Average Number of months'}",hAxis="{title:'Working Papers at REAL'}"))
print(bchart1,'chart')

```

--- .segue bg:indigo

## The REAL Network

--- 

## The REAL Mafia Network: Academic Influence

<iframe src="http://www.real.illinois.edu/networksVis/REALAcademicNet2/network/index.html#" heingt='600px'></iframe>

--- 

## The REAL Mafia Network: Friendship Influence

<iframe src="http://www.real.illinois.edu/networksVis/REALAcademicNet2/network/index.html#" heingt='600px'></iframe>

--- .segue bg:indigo

## The REAL Virtual Yearbook

--- 

<iframe src="http://www.real.illinois.edu/timeline/beta/" heingt='600px'></iframe>

---

## Semantic Analysis: Word Cloud

What is the first word that comes to your mind when you hear Geoffrey Hewings?

