---
title       : Creating a Virtual Yearbook of the REAL Mafia
subtitle    : Exploring its members' memories and connections
author      : Esteban Lopez
job         : UIUC PhD Candidate, REAL 'General'
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny, interactive, bootstrap]
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## Outline

>1. The Instrument
>2. Exploratory Analysis
>3. The REAL Mafia in a Network context
  - Academic
  - Friendship
>4. Spatial Analysis
>5. The REAL Virtual Yearbook
>6. Memories Semantic Analysis


--- 

## The Instrument

```{r echo=FALSE, results='asis', message=FALSE}
require(googleVis)
table1<-as.data.frame(cbind(c("Identification","Time in REAL","Academics with REAL","REAL Memories and Annecdotes"),c("Name, Country, Affiliation, etc.","Dates, Mafia role, General, sitting, etc.","Research areas, collaboration, influences, post-mafia work.","CU, UIUC, REAL, Geoff")))
names(table1)<-c("Section","Description")
table2<-gvisTable(table1)
cat(unlist(table2$html$chart))
print(table2,tag='chart')

```
<br>

- Sampled REAL Mafia: 400 (aprox.) e-mails sent
- Number of Respondents REAL Mafia: 104 responded surveys
- Number of attendants to this event: 120 aprox. 

---

## The 'Actual' Instrument

<iframe src="https://docs.google.com/forms/d/1B3qXUtLhqH7JSpo1zLH0DZeEzPPt0YIXEMp48NUA0eI/viewform?edit_requested=true" heingt='600px'></iframe>

--- .segue bg:indigo

## Exploratory Analysis

---  &vcenter

## Demographic Frequencies

```{r echo=FALSE, message=FALSE, results='asis',size=6}
require(stargazer)
setwd("/Users/estebanlopez/Documents/001 PhD Material/Work at REAL/25th-Anniversary/Timeline/realVirtualYearbook/")
data<-read.csv("data/data_exploratory.csv")
d2<-cbind(data[,4:6],data[,11])
colnames(d2)[4]<-"Mafia Type"
stargazer(as.matrix(ftable(summary(d2))),type="html",font.size="scriptsize")
```

---  &vcenter

## Initial Country


```{r echo=FALSE, message=FALSE, results='asis'}
setwd("/Users/estebanlopez/Documents/001 PhD Material/Work at REAL/25th-Anniversary/Timeline/realVirtualYearbook/")
data<-read.csv("data/data_exploratory.csv")

data$Current_Country2<-data$Current_Country
data$Country_Origin2<-data$Country_Origin
levels(data$Country_Origin2)[levels(data$Country_Origin2)=="Brasil"]<-"Brazil"
levels(data$Country_Origin2)[levels(data$Country_Origin2)=="US"]<-"USA"
levels(data$Country_Origin2)[levels(data$Country_Origin2)=="Espa\x96a"]<-"Spain"
levels(data$Country_Origin2)[levels(data$Country_Origin2)=="T\x9frkiye"]<-"Turkey"

pie3<-as.data.frame(round(table(data[,"Country_Origin2"]),2))
pie4<-gvisGeoChart(pie3,"Var1","Freq",options=list(width=800, height=500))
cat(unlist(pie4$html$chart))
print(pie4,tag="chart")
```

---  &vcenter

## Current Country


```{r echo=FALSE, message=FALSE, results='asis'}
setwd("/Users/estebanlopez/Documents/001 PhD Material/Work at REAL/25th-Anniversary/Timeline/realVirtualYearbook/")
data<-read.csv("data/data_exploratory.csv")

data$Current_Country2<-data$Current_Country
levels(data$Current_Country2)[levels(data$Current_Country2)=="US"]<-"USA"
levels(data$Current_Country2)[levels(data$Current_Country2)=="Estados Unidos"]<-"USA"
levels(data$Current_Country2)[levels(data$Current_Country2)=="U.S."]<-"USA"
levels(data$Current_Country2)[levels(data$Current_Country2)=="United States"]<-"USA"
levels(data$Current_Country2)[levels(data$Current_Country2)=="Champaign"]<-"USA"
levels(data$Current_Country2)[levels(data$Current_Country2)=="Espa\x96a"]<-"Spain"
levels(data$Current_Country2)[levels(data$Current_Country2)=="Brasil"]<-"Brazil"
levels(data$Current_Country2)[levels(data$Current_Country2)=="M\x8exico"]<-"Mexico"
levels(data$Current_Country2)[levels(data$Current_Country2)=="T\x9frkiye"]<-"Turkey"
levels(data$Current_Country2)[levels(data$Current_Country2)=="Brazil - USA"]<-"Brazil"
pie1<-as.data.frame(round(table(data[,"Current_Country2"]),2))
pie2<-gvisGeoChart(pie1,"Var1","Freq",options=list(width=800, height=500))
cat(unlist(pie2$html$chart))
print(pie2,tag="chart")
```

---  &vcenter

## FRIST most important research area at REAL.

```{r echo=FALSE, message=FALSE, results='asis'}
setwd("/Users/estebanlopez/Documents/001 PhD Material/Work at REAL/25th-Anniversary/Timeline/realVirtualYearbook/")
data<-read.csv("data/data_exploratory.csv")
pie1<-as.data.frame(round(table(data$research_1),2))
pie2<-gvisPieChart(pie1,options=list(width=700, height=600,legend="none"))
cat(unlist(pie2$html$chart))
print(pie2,tag="chart")
```

---  &vcenter

## SECOND most important research area at REAL.

```{r echo=FALSE, message=FALSE, results='asis'}
data<-read.csv("data/data_exploratory.csv")
pie1<-as.data.frame(round(table(data$research_2),2))
pie2<-gvisPieChart(pie1,options=list(width=700, height=600,legend="none"))
cat(unlist(pie2$html$chart))
print(pie2,tag="chart")
```

## Academic Productivity

```{r echo=FALSE, message=FALSE, results='asis'}
data<-read.csv("data/data_exploratory.csv")
pie1<-as.data.frame(round(table(data$research_2),2))
pie2<-gvisPieChart(pie1,options=list(width=700, height=600,legend="none"))
cat(unlist(pie2$html$chart))
print(pie2,tag="chart")
```

--- 

## The REAL Mafia in a Network Context

<iframe src="http://www.real.illinois.edu/networksVis/REALAcademicNet2/network/index.html#" heingt='600px'></iframe>
