---
title       : Creating a Virtual Yearbook of the REAL Mafia
subtitle    : Exploring its members' memories and connections
author      : Esteban Lopez
job         : UIUC PhD Candidate, REAL 'General'
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny, interactive, bootstrap]
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## Outline

>1. The Instrument
>2. Exploratory Analysis
>3. The REAL Mafia in a Network context
  - Academic
  - Friendship
>4. Spatial Analysis
>5. The REAL Virtual Yearbook
>6. Memories Semantic Analysis


--- .centrepre &vcenter

## The Instrument

```{r echo=FALSE, results='asis', message=FALSE}
require(googleVis)
table1<-as.data.frame(cbind(c("Identification","Time in REAL","Academics with REAL","REAL Memories and Annecdotes"),c("Name, Country, Affiliation, etc.","Dates, Mafia role, General, sitting, etc.","Research areas, collaboration, influences, post-mafia work.","CU, UIUC, REAL, Geoff")))
names(table1)<-c("Section","Description")
table2<-gvisTable(table1)
cat(unlist(table2$html$chart))
print(table2,tag='chart')
```

--- #dillinger

## The 'Actual' Instrument

<iframe src="https://docs.google.com/forms/d/1B3qXUtLhqH7JSpo1zLH0DZeEzPPt0YIXEMp48NUA0eI/viewform?edit_requested=true" heingt='600px'></iframe>

---  &vcenter

## Exploratory Analysis 

1. Please select the FRIST most important research area you focused on while you were at REAL.


---  &vcenter

## Exploratory Analysis 

1. Please select the FRIST most important research area you focused on while you were at REAL.


```{r echo=FALSE, message=FALSE, results='asis',size=5}
data<-read.csv("data/data_exploratory.csv")
pie1<-as.data.frame(round(prop.table(table(data$research_2)),2))
pie2<-gvisPieChart(pie1,options=list(
                    slices="{5: {offset: 0.2}, 10: {offset: 0.3}}",
                    pieHole=0.2, chartArea="{left:20,top:20,width:'200%',height:'200%'}", height="600px"))
cat(unlist(pie2$html$chart))
print(pie2,tag="chart")
```

--- #dillinger

## The REAL Mafia in a Network Context

<iframe src="http://www.real.illinois.edu/networksVis/REALAcademicNet2/network/index.html#" heingt='600px'></iframe>
